---
title: "cpi"
author: "Kurtis Pivert"
date: "5/19/2021"
output: 
    html_document:
        toc: TRUE
        theme: flatly
        code_folding: show
---


```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )
```

```{r Load Packages, include=FALSE}

require(knitr)
require(extrafont)
loadfonts(quiet = TRUE)
require(ggthemes)
require(ggtext)
require(gridExtra)
require(gridtext)
require(grid)
require(readxl)
require(patchwork)
require(tidyverse)

```

```{r Raw Data, message=FALSE}

df <- read_excel(
  here::here("00_data", "02_cpi/cpi.xls"), 
  skip = 10
  ) %>% 
  filter(
    observation_date >= lubridate::as_date("1959-01-01")
  )

cars <- read_csv(
  here::here("00_data", "02_cpi/cars.csv")
)

energy <- read_csv(
  here::here("00_data", "02_cpi/energy.csv")
)

gas <- read_csv(
  here::here("00_data", "02_cpi/gas.csv")
)

airfares <- read_csv(
  here::here("00_data", "02_cpi/airfares.csv")
)

furniture <- read_csv(
  here::here("00_data", "02_cpi/furniture.csv")
)

```


```{r Calculate Percent Change from Prev. Year}

pct_change_fun <- function(
  data, 
  num_column, 
  date_column = DATE, 
  date = as.Date("2020-01-01")
  ) {
  
  col_to_pct <- enquo(num_column)
  date_col <- enquo(date_column)
  
  pct_df <- data %>% 
    mutate(
      last_year = lag(!!col_to_pct, n = 12)
    ) %>% 
      rowwise() %>% 
  mutate(
    pct_change = (!!col_to_pct - last_year) / last_year
  ) %>% 
  ungroup() %>% 
  filter(
    !!date_col >= date
  )
  
  return(pct_df)
  
}

df <- df %>% 
  pct_change_fun(
    num_column = CPIAUCSL,
    date_column = observation_date,
    date = as.Date("1960-01-01")
  )

cars <- cars %>% 
  pct_change_fun(
    num_column = CUSR0000SETA02, 
    date_column = DATE
  )

energy <- energy %>% 
  pct_change_fun(
    num_column = CUSR0000SAH21
  )

furniture <- furniture %>% 
  pct_change_fun(
    num_column = CUSR0000SAH3
  )

gas <- gas %>% 
  pct_change_fun(
    num_column = CUSR0000SETB01
  )

airfares <- airfares %>% 
  pct_change_fun(
    num_column = CUSR0000SETG01
  )

```

## Motivation

## Initial Viz, Date, Description

For the third installment of my #wsj>ggplot2 project, I tried to recreate 
above-the-fold visualization illustrating the increse in CPI year over year (YOY). 

## Data Source 

Data came from FRED. 

## Initial Viz 

### Problems and Challenges  

* Axes and spacing
* First use of inset with [ggpatchwork](https://patchwork.data-imaginist.com/index.html).
* Aspect ratios and aligning axes

# Part 1: CPI Change YOY Area Chart

```{r}

cpi_viz <- ggplot(
  df, 
  aes(
    x = as.Date(observation_date), 
    y = pct_change
    )
  ) +
  # Base Theme -----------------------------------------------------------------
  theme_tufte(
    base_family = "Lato"
  ) +
  # Y Axis Text until 8% -------------------------------------------------------
  scale_y_continuous(
    breaks = seq(0, 0.08, 0.02),
    labels = as.character(seq(0, 8, 2))
  ) +
  # Y Axis Text 10%-14% --------------------------------------------------------
  annotate(
    geom = "text",
    x = as.Date("1978-09-01"),
    y = .105,
    label = "10",
    family = "Roboto Condensed",
    size = 3
  ) +
  annotate(
    geom = "text",
    x = as.Date("1978-9-01"),
    y = .125,
    label = "12",
    family = "Roboto Condensed",
    size = 3
  ) +
  annotate(
    geom = "text",
    x = as.Date("1979-02-01"),
    y = .145,
    label = "14%",
    family = "Roboto Condensed",
    size = 3
  ) +
  # Manually Create Y axis grid ------------------------------------------------
  # 0%
  geom_segment(
    aes(
      x = as.Date("1958-01-01"), 
      y = 0,
      xend = as.Date("2021-04-01"),
      yend = 0
        ),
    lwd = 0.05
  ) +
  # 2%
  geom_segment(
    aes(
      x = as.Date("1958-01-01"), 
      y = 0.02,
      xend = as.Date("2021-04-01"),
      yend = 0.02
        ),
    lwd = 0.05
  ) +
  # 4%
   geom_segment(
    aes(
      x = as.Date("1958-01-01"), 
      y = 0.04,
      xend = as.Date("2008-07-01"),
      yend = 0.04
        ),
    lwd = 0.05
  ) +
  # 6%
   geom_segment(
    aes(
      x = as.Date("1958-01-01"), 
      y = 0.06,
      xend = as.Date("1990-10-01"),
      yend = 0.06
        ),
    lwd = 0.05
  ) +
  # 8%
   geom_segment(
    aes(
      x = as.Date("1958-01-01"), 
      y = 0.08,
      xend = as.Date("1982-01-01"),
      yend = 0.08
        ),
    lwd = 0.05
  ) +
  # 10%
  geom_segment(
    aes(
      x = as.Date("1974-02-01"), 
      y = 0.10,
      xend = as.Date("1981-10-01"),
      yend = 0.10
        ),
    lwd = 0.05
  ) +
  # 12%
  geom_segment(
    aes(
      x = as.Date("1974-11-01"), 
      y = 0.12,
      xend = as.Date("1980-12-01"),
      yend = 0.12
        ),
    lwd = 0.05
  ) +
  # 14%
  geom_segment(
    aes(
      x = as.Date("1978-09-01"), 
      y = 0.14,
      xend = as.Date("1980-06-01"),
      yend = 0.14
        ),
    lwd = 0.05
  ) +
  # Manually Annotate X Axis Text ----------------------------------------------
  # 1960
  annotate(
    geom = "text",
    x = as.Date("1960-01-01"),
    y = -0.01,
    label = "1960",
    family = "Lato",
    size = 3
  ) +
  # 1970
  annotate(
    geom = "text",
    x = as.Date("1970-01-01"),
    y = -0.01,
    label = "'70",
    family = "Lato",
    size = 3
  ) +
  # 1980
  annotate(
    geom = "text",
    x = as.Date("1980-01-01"),
    y = -0.01,
    label = "'80",
    family = "Lato",
    size = 3
  ) +
  # 1990
  annotate(
    geom = "text",
    x = as.Date("1990-01-01"),
    y = -0.01,
    label = "'90",
    family = "Lato",
    size = 3
  ) +
  # 2000
  annotate(
    geom = "text",
    x = as.Date("2000-01-01"),
    y = -0.01,
    label = "2000",
    family = "Lato",
    size = 3
  ) +
  # 2010
  annotate(
    geom = "text",
    x = as.Date("2010-01-01"),
    y = -0.01,
    label = "'10",
    family = "Lato",
    size = 3
  ) +
  # 2020
  annotate(
    geom = "text",
    x = as.Date("2020-01-01"),
    y = -0.01,
    label = "'20",
    family = "Lato",
    size = 3
  ) +
  # Add April 2021 Point and Callout -------------------------------------------
   annotate(
    geom = "text", 
    x = as.Date("2021-03-01"), 
    y = 0.06, 
    label = "APRIL 2021", 
    family = "Roboto Condensed",
    hjust = 1
    ) +
  annotate(
    geom = "text", 
    x = as.Date("2021-03-01"), 
    y = 0.05, 
    label = "+4.2%", 
    family = "Roboto Condensed",
    hjust = 1,
    size = 6
    ) +
  geom_point(
    data = tibble(
      observation_date = as.Date("2021-04-01"),
      pct_change = 0.042
    ),
    aes(
      x = observation_date,
      y = pct_change
    ),
    size = .9
  ) +
  # Add Y Axis Text ------------------------------------------------------------
  annotate(
    geom = "text",
    x = as.Date("1958-01-01"),
    y = 0.11, 
    label = "Consumer price index,\nchange from previous year",
    hjust = 0,
    size = 3.5,
    family = "Roboto Condensed"
  ) +
  # Add Plot Title/Explanation -------------------------------------------------
  annotate(
    geom = "text",
    x = as.Date("1958-01-01"),
    y = 0.19, 
    label = "Consumer prices climbed in April\nby the most in nearly 13 years,\ndriven partly by sharp\nrises in prices for used\ncars and airline fares.",
    hjust = 0,
    size = 5,
    family = "Roboto"
  ) +
  # Add Inset/CPI Components Subhead -------------------------------------------
  annotate(
    geom = "text",
    x = as.Date("1986-01-01"),
    y = 0.23,
    label = "Monthly CPI for select categories, change from previous year",
    hjust = 0,
    size = 3, 
    family = "Roboto"
  ) +
  # Add Source Caption ---------------------------------------------------------
  labs(
    x = "", 
    y = "",
    caption = "Note: Seasonally Adjusted\nSource: Labor Department via the Federal Reserve Bank of St. Louis"
  ) +
  # Revise Theme Elements to match wsj style -----------------------------------
  theme(
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(
      vjust = - 0.8, 
      margin = margin(l = 20, r = -30),
      family = "Roboto Condensed"),
    plot.caption = element_text(
      hjust = 0, 
      color = "grey62",
      family = "Roboto Condensed Light"
      ) 
    ) +
  # Revise Plot Limits ---------------------------------------------------------
  expand_limits(
    x = as.Date("1958-01-01"),
    y = .24
  ) +
  # Plot the Data as Area ------------------------------------------------------
  geom_area(
    fill = "#0098DB",
    alpha = 0.5
  ) 

cpi_viz
  
```



## Part 2: CPI Components


### Used Cars and Trucks 

```{r}

a <- ggplot(
  cars %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position=position_dodge(9), 
  ) +
  expand_limits(
    y = c(-0.3, 0.25)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  # scale_x_date(
  #   date_breaks = "1 year",
  #   date_labels = "'%y"
  # ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "USED CARS/TRUCKS"
  ) +
  theme(
    legend.position = "none",
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 20)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2021-02-01"),
    y = 0.17,
    label = "+21%",
    size = 14,
    family = "Roboto Condensed"
  )
  
a

```

### Energy

```{r}

b <- ggplot(
  energy %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position=position_dodge(9), 
  ) +
  expand_limits(
     y = c(-0.3, 0.25)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "'%y"
  ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "HOUSEHOLD ENERGY"
  ) +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 20)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2021-02-01"),
    y = 0.17,
    label = "+6.4%",
    size = 14,
    family = "Roboto Condensed"
  )

b

```

### Airfares

```{r}

d <- ggplot(
  airfares %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position=position_dodge(9), 
  ) +
  expand_limits(
     y = c(-0.3, 0.25)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "'%y"
  ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "AIR FARES"
  ) +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 20)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2021-02-01"),
    y = 0.17,
    label = "+9.6%",
    size = 14,
    family = "Roboto Condensed"
  )

d

```


### Furniture

```{r}

c <- ggplot(
  furniture %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position=position_dodge(9), 
  ) +
  expand_limits(
     y = c(-0.3, 0.25)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "'%y"
  ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "FURNITURE"
  ) +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 20)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2021-02-01"),
    y = 0.17,
    label = "+3.5%",
    size = 14,
    family = "Roboto Condensed"
  )

c

```

### Gasoline

```{r}

e <- ggplot(
  gas %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position=position_dodge(9), 
  ) +
  expand_limits(
     y = c(-0.4, 0.5)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "'%y"
  ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "GASOLINE"
  ) +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 20)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2021-02-01"),
    y = 0.5,
    label = "+49.6%",
    size = 14,
    family = "Roboto Condensed"
  )

e

```

# Combine for Inset 

## Issues and Challenges  

* One
* Two

### Take One

```{r Combined Panel}

(a / c) | (b / d) | e + 
  plot_layout()

```

### Step One

```{r}

(a/c)|(b/d)

x <- (a/c)|(b/d)


```

### Step Two


```{r}

y <- x | e

```

### Step Three: Assemble Viz First Attempt


```{r}

cpi_viz +
  inset_element(
    y, 
    left = 0.5,
    bottom = 0.5,
    right = 1,
    top = 1
  )

# ggsave(
#   "cpi_r1.png",
#   width = 14,
#   height = 14 * 0.618,
#   units = "in",
#   dpi = 600,
#   type = "cairo"
# )


```


## Revise Ratios for Inset Figures

### Used Cars and Trucks---REVISED 

```{r}

a_rev <- ggplot(
  cars %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position = position_dodge(9), 
  ) +
  expand_limits(
    y = c(-0.3, 0.25)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "'%y"
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "USED CARS/TRUCKS"
  ) +
  theme(
    legend.position = "none",
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 13),
    axis.text.y = element_text(size = 10)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2020-10-01"),
    y = 0.17,
    label = "+21%",
    size = 5,
    family = "Roboto Condensed"
  )
  
a_rev

```

### Energy---REVISED

```{r}

b_rev <- ggplot(
  energy %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position=position_dodge(9), 
  ) +
  expand_limits(
     y = c(-0.3, 0.25)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "'%y"
  ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "HOUSEHOLD ENERGY"
  ) +
  theme(
    legend.position = "none",
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 13),
    axis.text.y = element_text(size = 10)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2020-10-01"),
    y = 0.17,
    label = "+6.4%",
    size = 5,
    family = "Roboto Condensed"
  )

b_rev


```

### Airfares---REVISED

```{r}

d_rev <- ggplot(
  airfares %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position=position_dodge(9), 
  ) +
  expand_limits(
     y = c(-0.3, 0.25)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  # scale_x_date(
  #   date_breaks = "1 year",
  #   date_labels = "'%y"
  # ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "AIR FARES"
  ) +
  theme(
    legend.position = "none",
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 13),
    axis.text.y = element_text(size = 10)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2020-10-01"),
    y = 0.17,
    label = "+9.6%",
    size = 5,
    family = "Roboto Condensed"
  )

d_rev

```


### Furniture---REVISED

```{r}

c_rev <- ggplot(
  furniture %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position=position_dodge(9), 
  ) +
  expand_limits(
     y = c(-0.3, 0.25)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "'%y"
  ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "FURNITURE"
  ) +
  theme(
   legend.position = "none",
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 13),
    axis.text.y = element_text(size = 10)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2020-10-01"),
    y = 0.17,
    label = "+3.5%",
    size = 5,
    family = "Roboto Condensed"
  )

c_rev

```

### Gasoline---REVISED

```{r}

e_rev <- ggplot(
  gas %>% 
    mutate(
      fill = case_when(
        pct_change > 0 & DATE < as.Date("2021-04-01") ~ "#0098DB",
        pct_change < 0 ~ "#958E83",
        pct_change > 0 & DATE == as.Date("2021-04-01") ~ "#0079AE" 
      )
    ), 
  aes(
    x = DATE, 
    y = pct_change,
    fill = fill
    )
  ) +
  geom_col(
    position=position_dodge(9), 
  ) +
  expand_limits(
     y = c(-0.5, 1.1)
  ) +
  scale_y_continuous(
    breaks = c(-.1, 0, .1),
    labels = c("\u201310", "0", "10%")
  ) +
  theme_tufte(
    base_family = "Lato"
  ) +
  geom_hline(
    yintercept = 0
  ) +
  geom_hline(
    yintercept = c(-.1, .1),
    lwd = 0.09
  ) +
  scale_fill_identity() +
  labs(
    x = "",
    y = "",
    title = "GASOLINE"
  ) +
  theme(
   legend.position = "none",
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    plot.title = element_text(
      family = "Roboto Condensed", 
      size = 13),
    axis.text.y = element_text(size = 10)
  ) +
  annotate(
    geom = "text",
    x = as.Date("2020-10-01"),
    y = 0.55,
    label = "+49.6%",
    size = 5,
    family = "Roboto Condensed"
  )


e_rev

```

### Assemble into Inset Viz---REVISED

```{r}

x_rev <- (a_rev / c_rev) | (b_rev / d_rev) 

y_rev <- x_rev | e_rev 

# y_rev <- y_rev +
#   plot_annotation(
#     title = "Monthly CPI for select categories, change from previous year",
#     theme = theme(
#       plot.title = element_text(family = "Roboto", size = 12)
#     )
#   )


cpi_viz +
  inset_element(
    y_rev, 
    left = 0.4,
    bottom = 0.4,
    right = .9,
    top = .9
  )

# ggsave(
#   "cpi_r3.png",
#   width = 9,
#   height = 6,
#   units = "in",
#   dpi = 600,
#   type = "cairo"
# )


```



```{r}

design <- "
  125
  345
"

cpi_inset <- a_rev + b_rev + c_rev + d_rev + e_rev + plot_layout(design = design)

cpi_viz +
  inset_element(
    cpi_inset, 
    left = 0.4,
    bottom = 0.4,
    right = .9,
    top = .9
  )

# ggsave(
#   "cpi_r12.png",
#   width = 10,
#   height = 7,
#   units = "in",
#   dpi = 600,
#   type = "cairo"
# )

```

